### 2014-05-07 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Add info on gas analyers; add placeholders for other equipment; add testing procedure

@@

@@

The following screens provide useful diagnostic information that can be sent to technical support:

\begin{itemize}
\item To display the version and serial number, press Main $\rightarrow$ F5 $\rightarrow$ F10.
\item To display flow diagnostics, press Main $\rightarrow$ F3.
\item To display raw voltage/channel values, press Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows.
\end{itemize}

@@

You can combine multiple videos into a multi-camera video using software such as Adobe Premiere or any other non-linear video editing software.

>>>>

\chapter{Data Acquisition System}

\chapter{Thermocouples}

\section{Uncertainty}

Uncertainty

\chapter{Bi-Directional Probes}

\section{Uncertainty}

Uncertainty

\chapter{Heat Flux Gauges}

\section{Uncertainty}

Uncertainty

@@

The CAI 602P Gas Analyzer can detect gas concentrations for CO$_2$, CO, and O$_2$ and output a voltage from 0~V to 5~V, which corresponds to 0~\% gas concentration to full-scale concentration.

\section{Internals}

The internal pump is located in the center of the chassis. The O$_2$ sensor is located under the foam cover. The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.

\section{Usage}

Important Note: The optimal pressure from the upstream sample and calibration gas is 0~psi! The internal gas analyzer components should never have an upstream pressure in excess of 2~psi. Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragms.

\begin{itemize}
\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage
\item Perform zero and span calibration on all analyzers.
    \begin{itemize}
    \item Flow N$_2$ and zero the CO$_2$, CO, and O$_2$ channels.
    \item Flow CO$_2$/CO calibration gas and span the CO$_2$ and CO channels.
    \item Use ambient air to span the O$_2$ channel.
    \end{itemize}
\item Set the upper ranges to the appropriate setting, which corresponds to 5~V on the output to the DAQ.
\item Measure the delay time for the sample gas to travel in the plumbing to the analyzer. You can do this by holding a CO$_2$ source near the sample port and measuring the time from exposing the sample port until the gas analyzer reads an increased value. Record this time so that the gas concentration can be offset later.
\item You are ready to record data to the DAQ.
\end{itemize}

\section{External Plumbing}

Calibration (span) gas (CO$_2$ and CO) $\rightarrow$ Bypass tee $\rightarrow$ Span gas inlet.

Sample tubes $\rightarrow$ Filter in dry ice (for scrubbing and cooling) $\rightarrow$ Sample pump (bypass value is on) $\rightarrow$ Sample inlet on gas analyzer $\rightarrow$ Outlet tube directed away from operator.

\section{Uncertainty}

Uncertainty

@@

\subsection{No Internal Flow}

If the flow drops to zero, then display the flow diagnostics by pressing Main $\rightarrow$ F3. Check the internal flow value for the three gases. If it is zero, then there might be a issue with the internal plumbing if the upstream pressure (from sample or calibration gases) exceeded 2~psi. Check power to the internal pump and ensure that it is operating.

\subsection{Bad Gas Concentration Readings}

If the channel is reading gas concentration values out of range or sporadic values, you may need to clean the internal sensor cell windows. Check the raw voltages in the analyzer setup by pressing Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows. The raw voltages should be around 1.0~V at 0~\% concentration, and 9~V at full-scale concentration. Refer to Section~10 of the CAI 600P User Manual for more information.

\subsection{Diagnostic Information}

The following screens provide useful diagnostic information that can be sent to technical support:
\begin{itemize}
\item To display the version and serial number, press Main $\rightarrow$ F5 $\rightarrow$ F10.
\item To display flow diagnostics, press Main $\rightarrow$ F3.
\item To display raw voltage/channel values, press Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows.
\end{itemize}

Refer to Section~10 of the CAI 600P User Manual for more information on maintenance and troubleshooting.

@@

You can combine multiple videos into a multi-camera video using software such as Adobe Premiere Pro or any other non-linear video editing software.

\appendix

\chapter{Testing Procedure}

\section{Initial Startup}

\begin{itemize}
\item Power on the following devices:
    \begin{itemize}
    \item Uninterruptible Power Supplies (UPSs)
    \item WiFi routers
    \item Hose flow / Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
    \item DAQs and laptops
    \item Gas analyzers (leave running as long as possible during testing)
    \item Digital video recorder (DVR)
    \item Bullet cameras
    \item Thermal imaging cameras (TICs) (check battery level)
    \item Digital video cassette recorders (DVCRs) (check battery level)
    \item GoPros (check battery level)
    \item Video cameras (check battery level)
    \end{itemize}
\end{itemize}

\section{Calibration}

\begin{itemize}
\item Synchronize time on DAQ computers and digital video recorder

\item Verify operation of all:
    \begin{itemize}
    \item Video channels
    \item DAQ channels
    \item Check toggle switches on TC-2095s for appropriate measurement device
    \item Gas analyzers
    \end{itemize}

\item Calibrate gas analyzers with zero and span gases

\item 1 minute calibration run to separate output file (cover BDPs, check TCs, etc.)

\end{itemize}

\section{Primary Testing Procedure}

\begin{itemize}
\item Verify testing procedure with all personnel
\item Safety checks

\item Power on gas analyzer pump

\item Turn on water for heat flux gauges

\item Check Arduino battery level
\item Power on Arduino data loggers

\item Start recording on:
    \begin{itemize}
    \item GoPros
    \item Video cameras
    \item DVCRs (Mobile TIC)
    \end{itemize}

\item Start synced recording on: [MARK DATE/TIME]
    \begin{itemize}
    \item DVR
    \item DAQ data
    \end{itemize}

\item 1 minute pre-test run (with all doors closed)

\item Begin test [MARK DATE/TIME]

\item Follow testing procedure

\item End test [MARK DATE/TIME]

\item Stop synced recording on: [MARK DATE/TIME]
    \begin{itemize}
    \item DAQ
    \item DVR
    \end{itemize}

\item Stop recording on:
    \begin{itemize}
    \item GoPros
    \item Video cameras
    \item DVCRs (Mobile TIC)
    \end{itemize}

\item Power off gas analyzer pump

\item Power off Arduino data loggers

\item Verify successful recording and operation of all DAQ channels in output file

\item Prepare for next test
\end{itemize}

\section{Data Dump}

\begin{itemize}
\item Retrieve data from:
    \begin{itemize}
    \item DAQ
    \item DVR
    \item GoPros
    \item Video cameras with digital media
    \item Arduinos
    \end{itemize}

\item Swap and label tapes from video cameras and DVCRs as needed

\item Make 3 copies of all data on external hard drives

\item Verify integrity of data

\item On return from trip, extract video from DVCRs
\end{itemize}

\section{Battery Charging}

\begin{itemize}
\item Charge all batteries on:
    \begin{itemize}
    \item Laptops
    \item Arduinos
    \item Bullet camera batteries
    \item TICs
    \item GoPros
    \item Video cameras
    \item DVCRs
    \end{itemize}
\end{itemize}
